% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Cosmin Stroe}
\newcommand{\CVTitle}{Software Developer}
\newcommand{\CVNote}{Created {\today}}
\newcommand{\CVWebpage}{https://github.com/cstroe}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=false,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
pdfborder={0 0 0},
breaklinks}

\pagestyle{fancy}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\thispagestyle{empty}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
%{17 Prime Avenue, Apt 37, Springfield, Pennsylvania 10111, USA}
%\par
{\UseSubTitleFont {\CVTitle}}
\par
\href{mailto:johndoe@example.com}
{cstroe@gmail.com}
%\,\SubBulletSymbol\,
%+1\,(555)\,101-1001
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%%%%%%%
%% OBJECTIVE       %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Objective}
{Objective}
{PDF:Objective}

\Gap
Seeking to deepen my knowledge of and experience with cloud systems operating at large scale, with a focus on efficiency, correctness, and maintainability.

\BigGap

%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\textbf{Senior Software Engineer}
\hfill
\DatestampYM{2020}{04} -- Current, 1 yr 6 mos

\href{https://www.uber.com/us/en/freight/}{Uber Freight}

\BigGap
\BulletItem Uber Freight SRE Team
\SubBulletItem Improve alerting and monitoring to reduce time-to-detection and time-to-mitigation of incidents.
\SubBulletItem Implement graceful failure modes and improve resilience to downstream system errors.
\SubBulletItem Update documentation, SOPs, runbooks, and dashboards to ease the burden on oncall engineers.
\SubBulletItem Foster a culture of knowledge sharing, ownership, and technical excellence with Freight engineers.

\BigGap
\Entry
\textbf{Staff Software Engineer}
\hfill
\DatestampYM{2016}{10} -- \DatestampYM{2020}{03}, 3 yrs 6 mos

\href{https://www.uptake.com}{Uptake Technologies Inc.}


\BigGap
\BulletItem
\DatestampYM{2019}{03} -- \DatestampYM{2020}{03} IoT Preventive Analytics Platform: Data Service
\SubBulletItem Part of Platform Data Team, developed and operated the data service for the platform.
\SubBulletItem Helped implement a performance monitoring framework to harden and scale the data service.

\Gap
\BulletItem
\DatestampYM{2017}{11} -- \DatestampYM{2019}{02} Data Ingestion Platform: Scaling and Hardening
\SubBulletItem Implement recovery mechanisms in streaming data pipelines.
\SubBulletItem Implement streaming processors monitoring via JMX and Telegraf.

\Gap
\BulletItem
\DatestampYM{2016}{10} -- \DatestampYM{2017}{10} Data Ingestion Platform: Implementation and Validation
\SubBulletItem Implemented a CI pipeline (Jenkins) to ensure software quality and timely feature delivery.
\SubBulletItem Integrating third-party applications into data ingestion and processing platform.
\SubBulletItem Load test data processing pipeline to ensure throughput SLAs.


\BigGap
\Entry
\textbf{Software Engineer}
\hfill
\DatestampYM{2014}{04} -- \DatestampYM{2016}{10}, 2 yrs 7 mos

\href{https://www.backstopsolutions.com}{Backstop Solutions Group}

\BigGap
\BulletItem
SaaS Platform to support professional and institutional investors
\SubBulletItem Day-to-day operations of Java EE web application.
\SubBulletItem Application performance monitoring, implemented AppDex metric for app.
\SubBulletItem YourKit profiling to identify and improve application performance.
\SubBulletItem Helped implement EHCache/Infinispan as an external caching solution.
\SubBulletItem Implemented SonarQube for static analysis of our code base to track and improve code coverage.
\BigGap

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.cs.uic.edu}
{University of Illinois at Chicago},
Chicago, Illinois, USA

\Gap
\BulletItem
Master of Science, Computer Science
\hfill
\DatestampY{2011} -- Incomplete, Thesis Required

\SubBulletItem
Course work GPA: 4.0

\Gap
\BulletItem
Bachelor of Science, Computer Engineering
\hfill
\DatestampY{2000} --
\DatestampY{2009}

\BigGap

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Professional Interests}
{Professional Interests}
{PDF:ProfessionalInterests}

\Entry
Artificial Intelligence,
Machine Learning,
Data Modeling and Analytics,
Cloud Platforms,
Stream Processing,
Distributed Systems,
Continuous Integration/Continuous Delivery,
Software Quality,
Platform Reliability.

\BigGap

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Preferred Languages}
{Preferred Languages}
{PDF:PreferredLanguages}

\Entry
Java,
Scala,
Go,
Rust (beginner).

\BigGap

%%%%%%%%%%%%%%%
%% SKILLS    %%
%%%%%%%%%%%%%%%

\Section
{Technologies\newline (alphabetical)}
{Technologies}
{PDF:Technologies}

\Entry
Ansible,
Cucumber,
Docker,
Elasticsearch,
Gradle,
Grafana,
InfluxDB,
Jenkins,
Jetty/Tomcat,
JVM,
Kafka,
Kafka Connect,
MySQL,
PostgreSQL,
Selenium,
Spring Boot,
Spring Framework,
SonarQube,
ZooKeeper.
\BigGap


\Section
{Last 3 books\newline I've read}
{Books}
{PDF:Books}

\hypersetup{
pdfborder={0 0 0.5},
urlbordercolor={0.6 0.8 1}
}

\Entry
\href{https://www.manning.com/books/rust-in-action}{Rust in Action} (in progress), 
\href{https://smile.amazon.com/gp/product/0201615983}{SSL and TLS: Designing and Building Secure Systems}, 
\href{https://smile.amazon.com/Always-Day-One-Titans-Forever/dp/0593083482}{Always Day One}

\BigGap


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
